|

### 2020-09-22 paper.Rmd
spelling

Following the processing described there, we tour the first 6 principal components, rescaled to have zero mean and unit variance. In Figure \ref{fig:pdfsense} we see that the sage display with $R = 10$ (Figure \ref{fig:pdfsense}, bottom), maintains the overall shape of the data seen using the default tour display (Figure \ref{fig:pdfsense}, top). The different physical process, shown in different colors, are indeed orthogonal in the parameter space, as can be seen most clearely by looking at the animations  available in the supplementary material.

@@

While the still views look very similar, comparing the tour animations (available in the supplementary material) revelas some differences between the display with trimming or tuning. When trimming by setting $R=1$ the focus is clearely on the center of the distribution, and most points get pushed out towards the circle of this maximum radius. On the other hand, tuning the display by setting $\gamma=20$ preserves the elliptical shape of the distribution, making it is easier to see correlation patterns.

>>>>

Following the processing described there, we tour the first 6 principal components, rescaled to have zero mean and unit variance. In Figure \ref{fig:pdfsense} we see that the sage display with $R = 10$ (Figure \ref{fig:pdfsense}, bottom), maintains the overall shape of the data seen using the default tour display (Figure \ref{fig:pdfsense}, top). The different physical process, shown in different colors, are indeed orthogonal in the parameter space, as can be seen most clearly by looking at the animations  available in the supplementary material.

@@

While the still views look very similar, comparing the tour animations (available in the supplementary material) reveals some differences between the display with trimming or tuning. When trimming by setting $R=1$ the focus is clearly on the center of the distribution, and most points get pushed out towards the circle of this maximum radius. On the other hand, tuning the display by setting $\gamma=20$ preserves the elliptical shape of the distribution, making it is easier to see correlation patterns.
